---
name: Rick
surname: Stoner
position: "Data Scientist"
address: "Dillsburg, Pennsylvania"
profilepic: "./images/frozen_motion_small.jpg"
# www: "RainBark.com"
email: "RLStoner@Gmail.com"
gitlab: KC3DRU
github: KC3DRU
linkedin: rick-stoner-39b1821
# orcid: 0000-0002-9604-3069
date: "`r format(Sys.time(), '%B %Y')`"
headcolor:  012EED  
aboutme: "Software developer working in the data science field focusing on <br/> data acquisition and preparation, process automation, and data visualization."
# docname: CV
output: 
  vitae::awesomecv:
  keep_tex: true

---


```{r setup, include=FALSE}
# install.packages("tinytex")
# tinytex::install_tinytex()
# install.packages("rsvg")

library(dplyr)                    # Data wrangling
library(emojifont)
library(fontawesome)
library(hrbrthemes)               # Better looking chart themes
library(ggplot2)                  # Plots on skills and mapping
library(kableExtra)
library(rmarkdown)
library(readODS)                  # Source data now comes from Libre Office worksheets
library(stringr)                  # String manipulation
library(tidyverse)
library(vitae) 

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

```


# \faIcon{briefcase} - Employment  

```{r EMPLOYMENT}

# Pull in the theme color from the YAML parms and use it in plots and 
# tables so that we have a consistent color theme.

myColor <- paste0('#',rmarkdown::metadata$headcolor)


work <- readODS::read_ods(path = './data/JobHistory.ods',
                         sheet = 1)
 
work %>%
  detailed_entries(
    with = role,
    what = company,
    why = details,
    when = glue::glue("{start_date} --> {end_date}",.na = ""),
    where = where
  )

```

# \faIcon{graduation-cap} - Education

```{r EDUCATION}
edu <- read.csv(file = './data/education.csv')

edu %>%
  detailed_entries(
    with = uni,
    what = degree,
    why = details,
    when = glue::glue("{startDate} --> {endDate}",.na = ""),
    where = loc
  )

```

# \faIcon{hat-wizard} - Skills

```{r SKILLS}
skills <- read_ods(path = './data/skills.ods',
                   sheet = 1)

skillSummary <- data.frame(Topic=character(), myList=character())


Topic_Areas <- unique(skills$`Topic Area`)

# Spin through the list of individual skills in each category.
# Build each skill into a string with a semicolon separating each entry.
for (x in 1:length(Topic_Areas)) {
  area = Topic_Areas[x]
  aList = ''
  y = 0
  yMax = length(skills$Topic[which(skills$`Topic Area` == area)])
  for (s in skills$Topic[which(skills$`Topic Area` == area)]) {
    
    y = y + 1
    if (y == yMax) {                # Skip semi for last entry on list
      newEntry = paste0(s)
    } else {
      newEntry = paste0(s, '; ')  
    }
    
    aList <- paste0(aList, newEntry)
  }
  skillSummary[nrow(skillSummary) + 1 , ] = c(area, aList)
}


skillSummary %>%
  detailed_entries(
    with = Topic,
    what = myList
  )

```

# \faIcon{medal} - Honors and Achievements

```{r AWARDS}
honors <- read_ods(path = './data/awards.ods',
                         sheet = 1)
honors %>%
  detailed_entries(
      with = Award,
    what = details,
    # why = details,
    when = startDate,
    where = From
  )

```

\newpage

# \faIcon{people-carry} - Community Service

```{r Service}

service <- read_ods(path = './data/CommunityService.ods',
                    sheet = 1)
service %>%
  detailed_entries(
    with = Charity,
    what = Role,
    # why = detail,
    when = glue::glue("{startDate} --> {endDate}",.na = "")
  )

```

# \faIcon{chalkboard-teacher} - Presentations

```{r Presentations}

projects <- read_ods(path = './data/presentations.ods',
                     sheet = 1)

projects %>%
  detailed_entries(
    with = Presentation,
    what = Description,
    # why = Why,
    when = WhenStart,
    where = Where
  )

```

# \faIcon{cogs} - Personal Projects

```{r PROJECTS, echo=FALSE, results='asis'}

projects <- read_ods(path = './data/projects.ods',
                     sheet = 1)

# This section will create a Kable table with information about 
# various geeky projects done at home.
projects %>%
  select('With', 'What') %>%
  rename('Project' = 'With', 'Description' = 'What') %>%
  kbl() %>%
  kable_styling(full_width = FALSE,  position = "left") %>%
  row_spec(0, color = myColor, bold = TRUE) %>%
  column_spec(1, width = "10em", border_left = TRUE) %>%
  column_spec(2, width = "30em", border_right = TRUE)

```



\newpage

\faIcon{star-half-alt} - Technical Self-Assessments
================

Rating my skills in various technologies on a scale of 1 to 10.

```{r,  fig.width = 8, fig.height = 5, fig.align = "center", out.width = "7.6in", out.height = "4.5in"}

# Set up a function to generate two skill plots at a time.
plotSkills <- function(Skill1, Skill2){
  skills %>%
    filter(str_detect(`Topic Area`, Skill1) |
             str_detect(`Topic Area`, Skill2)) %>%
    
        dplyr::group_by(`Topic Area`) %>%
  arrange((`Self-Assessment`), .by_group = TRUE) %>%
  mutate(ShortTopic = str_replace(Topic, '\\(.*\\)', '')) %>%
  mutate(ShortArea = str_replace(`Topic Area`, '\\(.*\\)', '')) %>%
  mutate(xord = factor(ShortTopic, levels = ShortTopic)) %>%
  
  ggplot( aes(x = xord, y=`Self-Assessment`)) +
  geom_segment(aes(x = xord, 
                   xend = xord, 
                   y = 0, 
                   yend = `Self-Assessment`),
               color="grey",
               alpha = 0.5, 
               size = 0.5) +
  geom_point(size=3,
             color = myColor, aes(alpha=0.5)) +
    geom_text(aes(label = `Self-Assessment`, 
                y = (`Self-Assessment` * 0.80)),
            hjust = 1,
            color = "black",
            position = position_dodge(0.5)) +
  scale_x_discrete() +
  coord_flip() +
    facet_wrap( ~ ShortArea, strip.position = "top", scales = "free_y", ncol = 2) +
    theme_ipsum() +
    theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position="none",
    axis.text.y = element_text(size = 12),
    axis.text.x = element_blank(),
    title = element_text(size = 13, color = myColor)
  ) +
    ggtitle(label = "Technical Skills Self-Assessment") +
  xlab("") +
  ylab("")
}

# Generate two plots at a time.
plotSkills('Program', 'Markup')
plotSkills('Database', 'Interch')
plotSkills('Text', 'Vers')
plotSkills('Operat', 'Single')

```


\pagebreak


\faIcon{globe-americas} - Talking to the world - One QSO at a time
============================

The amateur radio hobby provides a rich source of geospatial data points.  The hobby involves using your
radio equipment to talk to other operators throughout the world via various modes of communication: voice,
Morse Code, or numerous digital modes.  Each successful contact is called a QSO.  In the past, operators would
exchange custom postcards with the date and signal quality of the chat.  Often operators would use a large map
and pushpins to mark their successes.  Today, we mostly use electronic logs.

I used my electronic contact log's data to generate the map below which shows the locations of operators that I 
successfully spoke with using a voice mode.

---
```{r edu_plot,fig.align='center', fig.width=6.5, fig.height=2.7, fig.showtext=TRUE}

data <- read_delim('data/contactLog.csv', delim = '\t') %>%
  filter(mode %in%  c('SSB', 'FM', 'AM')) %>%
  filter(lat > -60)

grid_connections <- data %>%
  mutate(Maiden4 = substr(maiden, 1, 4)) %>%
  dplyr::group_by(Maiden4, mylat, mylon) %>%
  dplyr::summarise(Mh4_lat = mean(lat),
                   Mh4_lon = mean(lon)) %>%
  dplyr::ungroup()



world <- map_data("world")

world %>% filter(`region` != "Antarctica") %>%     # Focus on the other parts
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(fill="white", color = "#dcdcdc", size=0.05, alpha = 0.1) +
  geom_curve(data = grid_connections, 
             aes(x = mylon, 
                 xend = Mh4_lon,
                 y = mylat,  
                 yend = Mh4_lat), 
             alpha=0.1, 
             size=0.5,
             color = myColor,
             inherit.aes = FALSE) +
  theme_void() +
  theme(plot.background=element_rect(fill="white",linetype = 0),
        legend.position="none",
        axis.text = element_blank(),
        axis.line = element_blank(),
        panel.grid = element_blank(),
        # panel.border = element_rect(linetype = 0),
        plot.caption = element_text(size = 6,
                          hjust = 0.92, 
                          margin = margin(t = 0.2,
                                          b = 0,
                                          unit = "cm"), 
                                  color = "black"), 
        title = element_text(size = 14, color = myColor, family =) ) +
    ggtitle(label = "KC3DRU Contact Log",
            subtitle = "Direct voice contacts using single sideband mode") +
  labs(caption = "Data source: ADIF logbook with Maidenhead Grid Square coordinates transformed to Lat. / Lon. via Python.") +
    xlab("") +
  ylab("") +
  coord_equal()

```

\bigskip
\bigskip


\faIcon{microscope} - About this CV
============================

This curriculum vitae was generated in RMarkdown using Mitchell O'Hara-Wild's library "Vitae" *(https://pkg.mitchelloharawild.com/vitae/)* and a couple LaTeX statements here and there to help with pagination.  Bryan Jenks has a great video showing how to get started with Mitchell's library  *(https://www.youtube.com/watch?v=cMlRAiQUdD8)*.  I pulled in the custom LaTeX class file from Lorena Abad's GitHub *(https://github.com/loreabad6/R-CV)*.

My 'Twenty Second' brief resume is available in my GitHub repo  https://github.com/KC3DRU/CV/Resume20Seconds.pdf . 

